\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot,
    top=2 cm,
    bottom=2 cm,
    left=2 cm,
    right=2 cm,
    footskip=1.0 cm,
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 0, 0}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Harshwardhan Patil's CV},
    pdfauthor={Harshwardhan Patil},
    pdfcreator={LaTeX with RenderCV},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[pscoord]{eso-pic}
\usepackage{calc}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}
\usepackage{iftex}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\usepackage{charter}

\raggedright
\AtBeginEnvironment{adjustwidth}{\partopsep0pt}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\topskip}{0pt}
\setlength{\columnsep}{0.15cm}
\pagenumbering{gobble}

\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]

\titlespacing{\section}{-1pt}{0.3 cm}{0.2 cm}

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\newenvironment{highlights}{\begin{itemize}[topsep=0.10 cm, parsep=0.10 cm, partopsep=0pt, itemsep=2pt, leftmargin=10pt]}{\end{itemize}}
\newenvironment{onecolentry}{\begin{adjustwidth}{0 cm}{0 cm}}{\end{adjustwidth}}
\newenvironment{twocolentry}[2][]{\onecolentry\def\secondColumn{#2}\setcolumnwidth{\fill, 4.5 cm}\begin{paracol}{2}}{\switchcolumn \raggedleft \secondColumn\end{paracol}\endonecolentry}

\begin{document}

\newcommand{\AND}{\unskip\cleaders\copy\ANDbox\hskip\wd\ANDbox\ignorespaces}
\newsavebox\ANDbox
\sbox\ANDbox{$|$}

\begin{center}
    {\fontsize{25 pt}{25 pt}\selectfont Harshwardhan Patil}

    \vspace{5 pt}
    \normalsize
    \faMapMarker*\ Arlington, TX\hspace{1.5em}
    \faEnvelope\ \href{mailto:work.harshwardhanpatil@gmail.com}{work.harshwardhanpatil@gmail.com}\hspace{1.5em}
    \faPhone\ \href{tel:8179389288}{817-938-9288}\hspace{1.5em}
    \faLinkedin\ \href{https://www.linkedin.com/in/harshwardhanpatil23/}{LinkedIn}\hspace{1.5em}
    \faGithub\ \href{https://github.com/buffden}{GitHub}
\end{center}

\vspace{0.3 cm}
\newcommand{\educationentry}[4]{%
  \noindent\textbf{#1} \hfill \textit{#2}\\
  \textit{#3} \\
  #4
}
\section{Overview}
\textbf{Frontend-focused Full-Stack Developer} with 3+ years of experience building scalable Angular applications, optimizing CI/CD workflows, and mentoring junior engineers across Agile teams.

\section{Education}
\educationentry
    {University of Texas at Arlington}
    {Expected May 2026}
    {Master’s in Software Engineering}
    {
    \begin{highlights}
        \item \textbf{Relevant Coursework:} System Design, Software Testing, Cloud Computing, AI/ML with Python, Distributed Systems
        \end{highlights}
    }
    
\section{Technical Skills}
\begin{onecolentry}
    \item \textbf{Programming Languages}: TypeScript, JavaScript, Java, Python, SQL, Bash
    \item \textbf{Frameworks \& Libraries}: Angular, Spring Boot, Spring Security, Spring JDBC, Spring Data JPA, Node.js, Flask, Streamlit, Pandas, D3.js
    \item \textbf{Front-End Development}: Angular CLI, Angular Material, HTML, CSS, RxJS, Lazy Loading, Routing Guards, Responsive Design, Component Reusability
    \item \textbf{Back-End Development}: RESTful API Design, Microservices, Database Migration (AWS Aurora), Apache Kafka (basics), DTO Pattern, Clean Architecture, JWT Authentication
    \item \textbf{Architecture \& Design}: System Design, High-Level Design (HLD), Low-Level Design (LLD), UML (Class, Sequence, Activity Diagrams), SOLID Principles, Domain-Driven Design (DDD), Event-Driven Architecture (EDA), MVC, Modular Monoliths
    \item \textbf{Cloud \& DevOps}: AWS (EC2, ECS, S3, RDS, Lambda, Aurora), Docker, Kubernetes (basic), Jenkins, GitHub Actions, GitLab CI/CD, Spinnaker, Terraform
    \item \textbf{CI/CD \& Deployment Tools}: Docker Compose, Nginx, Apache HTTP Server
    \item \textbf{Databases \& Tools}: PostgreSQL, MySQL, MongoDB, Amazon DynamoDB, Redis, pgAdmin, MongoDB Compass, DBeaver
    \item \textbf{Testing \& Debugging}: Jasmine, PyTest, JUnit, SonarQube, SonarQube Cloud, Postman Tests, Chrome Dev Tools
    \item \textbf{Security \& Auth}: Spring Security, JWT-based Authentication, OAuth 2.0 (basic), CORS, HTTPS, CSRF Protection, Role-Based Access Control (RBAC)
    \item \textbf{Other Tools}: Git, Postman, Jira, VS Code, IntelliJ IDEA, Notion, Figma, Draw.io, Mermaid AI
    \item \textbf{Terminal \& Productivity Tools}: Tmux, Vim, Zsh, CLI Debugging, Homebrew
     \item \textbf{Collaboration \& Leadership}: Agile, Scrum, Sprint Planning, Mentoring, DevOps Advocacy, Technical Presentations, Documentation, Continuous Learning and Adaptability
\end{onecolentry}



\newcommand{\experienceentry}[4]{%
  \noindent\textbf{#1} \hfill \textit{#2}\\
  \textit{#3} \\
  #4
  \vspace{0.3cm}
}

\section{Professional Experience}

\experienceentry
  {Software Engineer, Clarivate Analytics -- Bangalore, India}
  {Aug 2023 -- Aug 2024}
  {Full-Time}
  {
    \begin{highlights}
        \item Designed and developed a fully reusable, configurable table component in \textbf{Angular}, enabling dynamic column ordering, user preference storage, and real-time updates. Integrated chips, links, buttons, and side panels for rich interactions, plus seamless Excel export using \textbf{Apache POI}, reducing table code duplication by \textbf{60\%+}.

        \item Built a sophisticated dynamic filter system with a two-pane popup UI, delivering real-time interdependent filtering logic where selected options narrow down others automatically. Added a robust reset-to-last-applied-state feature, intuitive chips for active filters, and a ‘Clear All’ function, enhancing data exploration usability.
        
        \item Architected generic, reusable \textbf{D3.js} components for bar, stacked bar, line, and pie charts with abstracted chart data preparation and configuration methods. Enabled flexible injection of chart options for legends, tooltips, labels, and colors, driving consistent, maintainable visualizations across modules.
        
        
        \item Developed robust \textbf{PPT/PDF export functionality} using \textbf{RxJS forkJoin}, resolving large report download performance issues and improving content clarity for business users.
        
        \item Refactored legacy modules across DCF and Insights to align with modern \textbf{Angular patterns}, enhancing maintainability, scalability, and component reuse.
        
        \item Maintained full ownership of \textbf{production deployments} for over \textbf{20 months}, executing releases without error across high-stakes systems.
        
        \item Investigated and resolved complex production issues using \textbf{PostgreSQL logs}, \textbf{Sentry}, and \textbf{Chrome DevTools}, contributing to faster resolution and improved product stability.
        
        \item Followed \textbf{GitFlow branching} and conducted rigorous \textbf{peer code reviews}, promoting clean architecture and reducing defects in merged PRs.
        
        \item Wrote and maintained \textbf{unit test coverage of 85\%+} across UI modules, ensuring safe and testable feature rollouts.
        
        \item Configured \textbf{Spinnaker pipelines} and authored reusable \textbf{Terraform modules} to automate infrastructure provisioning and \textbf{production deployments}, enabling rapid rollout of Dockerized applications from \textbf{Bitbucket} across \textbf{AWS environments}.
        
        \item Mentored \textbf{2 junior Angular developers} via weekly pairing sessions, architecture reviews, and growth tracking to accelerate onboarding and improve team velocity.
        
        \item Volunteered on a \textbf{Generative AI POC} while managing full sprint deliverables, showcasing adaptability and initiative in cross-functional innovation.
        
        \item Assisted teammates with complex features like \textbf{tree filters}, \textbf{bookmarks}, and export logic, driving collaborative success across frontend and backend layers.
        
        \item Refactored export and \textbf{qualitative data components} in DCF and Company Insights modules, converting them into modular, reusable units that accelerated development for \textbf{3+ future features} and ensured long-term maintainability.
        
        \item Implemented high-resolution \textbf{qualitative data rendering}, including \textbf{pie chart visualizations}, to improve analytical readability in Company Insights reports during \textbf{User UAT}, reducing manual feedback cycles by \textbf{30\%}.
        
    \end{highlights}

  }

\experienceentry
  {Associate Software Engineer, Clarivate Analytics -- Bangalore, India}
  {Aug 2021 -- Jul 2023}
  {Full-Time}
  {
    \begin{highlights}
    \item Designed and implemented reusable \textbf{spike charts} and \textbf{advanced search functionality} using \textbf{Angular} and \textbf{D3.js} for the \textbf{CGI product} (Tickets: \textbf{LSN-12460}, \textbf{LSN-12631}), improving data usability and reducing development effort.

\item Delivered user-focused features including \textbf{bookmarkable tables}, and \textbf{saved searches}, enhancing end-user experience across multiple modules.

\item Took ownership of \textbf{15+ production releases} with \textbf{zero deployment errors} over 3 consecutive quarters, ensuring high availability and zero rollback scenarios.

\item Authored detailed \textbf{documentation} on reusable chart implementation and release procedures, reducing \textbf{onboarding and KT time by ~50\%} for new team members.

\item Supported \textbf{backend and QA teams} with early environment testing and collaborative debugging, enabling faster defect detection and reducing QA cycles.

\item Completed advanced training in \textbf{Angular}, \textbf{D3.js}, and \textbf{Jasmine}, translating learnings into improved UI architecture and increased test coverage.

\item Wrote \textbf{Jasmine unit tests} for frontend modules, achieving high code quality with minimal post-release bugs.

\item Participated in \textbf{sprint planning}, \textbf{refinement}, and \textbf{demos}, consistently delivering quarterly goals with \textbf{near-zero slippage} and strong sprint execution.

\item Played a key role in \textbf{release process development} for \textbf{DCF}, coordinating with UI, backend, and QA to standardize pre-deployment checks and ensure consistent release quality alongside CGI responsibilities.

\item Contributed to complex filtering logic in \textbf{PST module} features like \textbf{tree filters} and \textbf{bookmarks}, collaborating with cross-functional teams to align logic implementation with evolving product requirements.

    \end{highlights}

  }
\newcommand{\projectentry}[4]{%
  \noindent\textbf{#1} \hfill \textit{#2}\\
  \textit{#3} \\
  #4
  \vspace{0.3cm}
}
\section{Projects}
  
\projectentry
  {Battle Arena – Multiplayer Artillery Game Platform}
  {May 2024 - Present}
  {GitHub · Angular, Phaser 3, Spring Boot, Node.js, MongoDB, WebSockets, Docker, AWS}
  {
    \begin{highlights}
    \item Architected and implemented a full-stack real-time multiplayer game platform inspired by Pocket Tanks, supporting modular player types (tanks, wizards, mechs) and pluggable arena systems.
    \item Designed a scalable microservices architecture, separating concerns across services: auth-service, user-profile-service, leaderboard-service, matchmaking-service, game-engine-service.
    \item Integrated Phaser 3 game engine within Angular 17 for smooth turn-based 2D artillery gameplay inside a browser.
    \item Developed backend with Spring Boot REST APIs for user management and leaderboards, and Node.js + Socket.io services for real-time matchmaking and gameplay physics.
    \item Used MongoDB for flexible storage of user profiles, match histories, and ranking data, enabling easy schema evolution.
    \item Containerized all services with Docker, orchestrated via docker-compose, enabling one-command local development and future CI/CD scalability.
    \item Implemented JWT-based authentication, modular Angular routing, and dynamic UI features like dashboards, player stats, and leaderboards.
    \end{highlights}
  }

\projectentry
  {Better Finance – Hackathon Project (UTA)}
  {Hackathon - Mar 2025}
  {GitHub · Angular, Flask, Streamlit, PostgreSQL, Plaid API, Docker}
  {
    \begin{highlights}
    \item Developed in a team of 3 during a university hackathon; built a full-stack platform for AI-powered personal finance management.
    \item Integrated Plaid API for secure bank account linking and real-time transaction syncing.
    \item Implemented OCR-based invoice processing and financial advice chatbot using AI/ML models.
    \item Designed Streamlit UI for quick access to account overviews, transaction analytics, and budget alerts.
    \item Containerized services using Docker for quick deployment and hackathon-scale setup.
    \end{highlights}
  }



  \projectentry
  {Employee Management System (EMS)}
  {Dec 2024 – Present}
  {Spring Boot, Angular, PostgreSQL, AWS, Docker, Jenkins}
  {
    \begin{highlights}
      \item Built robust Spring Boot REST APIs for employee/department management, dashboard metrics, and real-time data filtering (pagination, sorting, dynamic POST queries).
      \item Deployed PostgreSQL on AWS RDS and backend on AWS EC2 using .env-based secure auth and custom firewall rules.
      \item Containerized services using Docker and an automated CI/CD pipeline with Jenkins for both frontend (Angular) and backend (Spring Boot).
      \item Implemented CORS, centralized error handling, and DTO-layered clean architecture.
      \item Designed and connected metric cards API and department/employee charts (Chart.js).
      \item Future-proofed system with modular microservice-friendly design, aligning with Clean Architecture patterns.
    \end{highlights}
  }

% \projectentry
%   {AI-Powered Personal Finance Manager}
%   {Feb – April 2025}
%   {Flask, Streamlit, Python, Plaid API, AWS EC2, Docker}
%   {
%     \begin{highlights}
%       \item Engineered Flask-based REST API microservices to interact with Plaid's Banking API for secure token exchange, account linking, and transaction retrieval.
%       \item Deployed backend on AWS EC2 and used Docker to containerize services for portability and scaling.
%       \item Implemented advanced financial insights (monthly trends, category-based expenses) using Python and Pandas.
%       \item Built Streamlit frontend with a 3-step user journey (link bank $\Rightarrow$ fetch transactions $\Rightarrow$ view insights).
%       \item Secured sandbox production access and submitted compliant API usage proposal to Plaid.
%     \end{highlights}
%   }
\section{Certifications}
\begin{onecolentry}
    \item AWS Certified Cloud Practitioner – CLF-C02 (2025)
    \item AWS Certified Developer – Associate – DVA-C02 (2025)
    \item AWS Certified Solutions Architect – Associate – SAA-C03 (2025)
    \item Oracle Certified Professional: Java SE 17 Developer – 1Z0-829 (2025)
    \item AWS Skill Builder Badges: Cloud Essentials, Serverless on AWS, Cloud Quest Practitioner, AI Services, ML Basics (2025)
\end{onecolentry}


\end{document}