\documentclass[10pt, letterpaper]{article}

% --- Packages ---
\usepackage[
    ignoreheadfoot,
    top=0.7cm,
    bottom=0.7cm,
    left=0.7cm,
    right=0.7cm,
    footskip=0.5cm,
]{geometry}
\usepackage{titlesec}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 0, 0}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Harshwardhan Patil's CV},
    pdfauthor={Harshwardhan Patil},
    pdfcreator={LaTeX with RenderCV},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[scaled=0.92]{helvet}
\renewcommand\familydefault{\sfdefault}
\usepackage{changepage}
\usepackage{paracol}

% --- Page setup ---
\raggedright
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\pagenumbering{gobble}

% --- Section formatting ---
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{-1pt}{0.3cm}{0.2cm}

% --- Lists ---
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\newenvironment{highlights}{\begin{itemize}[itemsep=1pt, parsep=0pt, topsep=0pt, partopsep=0pt, leftmargin=10pt]}{\end{itemize}}
\newenvironment{onecolentry}{
  \begin{adjustwidth}{0cm}{0cm}
  \begin{itemize}[itemsep=1pt, parsep=0pt, topsep=0pt, partopsep=0pt, leftmargin=10pt]
}{
  \end{itemize}
  \end{adjustwidth}
}
\begin{document}

% --- Header ---
\begin{center}
    {\fontsize{20pt}{20pt}\selectfont \textbf{Harshwardhan Patil}} \\[6pt]
    \faMapMarker* Houston, TX \hspace{1.2em}
    \faEnvelope\ \href{mailto:work.harshwardhanpatil@gmail.com}{work.harshwardhanpatil@gmail.com} \hspace{1.2em}
    \faPhone\ \href{tel:8179389288}{817-938-9288} \hspace{1.2em}
    \faLinkedin\ \href{https://www.linkedin.com/in/harshwardhanpatil23/}{LinkedIn} \hspace{1.2em}
    \faGithub\ \href{https://github.com/buffden}{GitHub} \hspace{1.2em}
    \faGlobe\ \href{https://buffden.com/}{Portfolio}

\end{center}

{\small
\vspace{-0.5cm}
% --- Summary ---
\section{Summary}
\vspace{-0.1cm}
Full-Stack Engineer with \textbf{5+ years of experience} building scalable, distributed systems and high-performance APIs across frontend, backend, and cloud. Skilled in \textbf{system design}, CI/CD on AWS, production monitoring, and delivering \textbf{fault-tolerant, data-consistent services} at scale in \textbf{Agile} environments.

\vspace{-0.2cm}
% --- Technical Skills ---
\section{Technical Skills}
\vspace{-0.1cm}
\begin{onecolentry}
    \item \textbf{Languages \& Frameworks:} Java, TypeScript, JavaScript, SQL, Spring Boot, Angular, Node.js, Python, FastAPI
    \item \textbf{Cloud \& DevOps:} AWS (EC2, ECS, S3, RDS, CloudFront, ALB, Secrets Manager, Lambda), Docker, Jenkins, Git, GitHub Actions, Nginx, Cloudflare
    \item \textbf{Databases:} PostgreSQL, Redis, MySQL, Neo4j, Elasticsearch, MongoDB, Schema design, Database indexing, Query optimization, Caching strategies
    \item \textbf{Testing \& Security:} JUnit, Mockito, Jasmine, Vitest, ESLint, SonarQube, Postman, JWT, RBAC, HTTPS/TLS, CORS, CSRF/XSS protection
    \item \textbf{Design \& Architecture:} System Design, Design Patterns, SOLID principles, Distributed backend services, Concurrency handling, Session management
    \item \textbf{AI \& ML:} Spring AI, OpenAI API, Prompt Engineering, Embeddings, Vector Search, RAG Pipelines, pgvector
    % \item \textbf{AI \& ML:} Spring AI, OpenAI API, Prompt Engineering, RAG Pipelines, Embeddings, Vector Search, pgvector, Tool Calling, Multi-Agent Workflows, LangChain/LangGraph, MCP, LLM Evaluation, AI Observability, Prompt Injection Detection    

\end{onecolentry}


\vspace{-0.2cm}
% --- Professional Experience ---
\section{Professional Experience}

\vspace{-0.1cm}
\textbf{Software Engineer, Clarivate Analytics} -- Bangalore, India \hfill \textit{Aug 2023 - Jul 2024} \\
\begin{highlights}
    \item Developed scalable Spring Boot REST APIs with DTO contracts and standardized error handling, reducing breaking changes by \textbf{30\%} across releases.
    \item Implemented \textbf{JWT}-based multi-session management across backend services, capping concurrent logins at 12 per user with token invalidation on breach.
    \item Optimized \textbf{PostgreSQL} schemas with composite indexing across reporting and search workloads for drug and patent datasets, cutting full scans.
    \item Containerized and deployed microservices to \textbf{EC2} using Docker and Jenkins \textbf{CI/CD} pipelines, supporting \textbf{50+ production releases} with \textbf{zero rollbacks}.
    \item Enforced role-based access control across backend and frontend layers, applying tiered and region-based data visibility for \textbf{10+ access variants}.
    \item Implemented low-latency \textbf{Elasticsearch}-powered typeahead and autocomplete, improving search response times by \textbf{40\%} over large-scale datasets.
    \item Developed dynamic PPT and PDF export pipelines using \textbf{PptxGenJS} and \textbf{jsPDF}, generating \textbf{100+ customized reports} with user-selected filters.
    \item Optimized \textbf{PostgreSQL} query logic for PPT export, decoupling bulk multi-filter chart fetching from single-chart UI rendering to reduce DB round-trips.
    \item Achieved \textbf{90\%} test coverage using \textbf{JUnit} and \textbf{Mockito} for backend and \textbf{Jasmine} for Angular, covering unit, branch, and line coverage across all modules.
\end{highlights}

\vspace{0.1cm}
\textbf{Associate Software Engineer, Clarivate Analytics} -- Bangalore, India \hfill \textit{Aug 2021 - Jul 2023} \\
\begin{highlights}
    \item Integrated \textbf{Elasticsearch} into Spring Boot, enabling advanced full-text queries across \textbf{millions of drug records} and reducing search latency by \textbf{30\%}.
    \item Migrated \textbf{5+ core business flows} from Angular 8 to \textbf{Angular 13}, rebuilding components with a modular architecture and improved state management.
    \item Built secure request-handling across backend services using \textbf{Spring Security}, \textbf{CORS/CSRF}, and input validation to guard against unauthorized access.
    \item Improved responsiveness of data-heavy chart and table views by \textbf{20--25\%} through lazy loading, \textbf{RxJS} streams, and Angular lifecycle optimizations.
    \item Reduced page load times by \textbf{20\%} by applying component-level \textbf{OnPush} change detection and optimizing data-fetching patterns across data-heavy views.
    \item Built \textbf{D3.js} chart components with grouping and filtering aggregations for \textbf{Angular}, powering \textbf{15+ analytics views} across drug intelligence dashboards.
    \item Architected a configurable \textbf{Angular} table framework with sorting, pagination, and filters; adopted across \textbf{3 internal teams}, cutting duplication by \textbf{50\%}.
\end{highlights}

\vspace{-0.2cm}
% --- Education ---
\section{Education}
\vspace{-0.1cm}
\textbf{University of Texas at Arlington}\hspace{3.3em}\textit{Master's in Software Engineering}\hspace{3.3em}\textit{GPA: 3.6 / 4.0} \hfill \textit{Aug 2024 - May 2026} \\

\vspace{-0.2cm}
% --- Projects ---
\section{Projects}

\vspace{-0.1cm}
\textbf{TinyURL — URL Shortener} \hspace{1em}\href{https://github.com/Buffden/tinyurl-api}{\faGithub}\hspace{0.6em}\href{https://tinyurl.buffden.com/}{\faLink} \hfill \textit{Feb 2026 - Mar 2026} \\
\textit{Production-grade URL shortening service with QR code generation, link expiry, and a fully automated cloud deployment pipeline.} \\
\textbf{Tools: } Spring Boot, Angular, PostgreSQL, AWS (EC2, RDS, S3, CloudFront, ALB), Docker, Cloudflare, Nginx, Lambda, EventBridge, SQS DLQ, CloudWatch \\
\begin{highlights}
    \item Designed \textbf{6-layer request path} across Cloudflare, CloudFront, ALB, Nginx, Spring Boot, and PostgreSQL, separating SPA delivery from API and redirects.

    \item Hardened API traffic with \textbf{Nginx rate limits}, \textbf{Bucket4j token buckets}, \textbf{layer-7} bot/scanner filters, per-IP size caps, and strict \textbf{HSTS/CSP} secure headers.

    \item Designed serverless EC2/RDS scheduler with Lambda, EventBridge, CloudWatch alarms, SNS, and SQS DLQ, reducing monthly cloud cost by \textbf{\textasciitilde40\%}.

    \item Built zero-SSH \textbf{CI/CD} with GitHub Actions, AWS OIDC, SSM RunCommand, Docker smoke tests, cosign signing, and auto CloudFront cache invalidation.

\end{highlights}
\vspace{0.1cm}


\textbf{diagram-sync — Diagram-as-Code CLI} \hspace{1em}\href{https://github.com/Buffden/diagram-sync}{\faGithub}\hspace{0.6em}\href{https://www.npmjs.com/package/diagram-sync}{\faLink}\hspace{0.6em}\faDownload\hspace{0.3em}2,824 \hfill \textit{May 2026 - Present} \\
\textit{Published npm package that renders architecture diagrams from 7 source formats into versioned SVG/PNG outputs via \texttt{npx diagram-sync}.} \\
\textbf{Tools: } TypeScript, Node.js, Vitest, ESLint, GitHub Actions \\
\begin{highlights}
    \item Engineered \textbf{provider-registry architecture} mapping 14+ file extensions to isolated rendering adapters with runtime graceful degradation on missing tools.

    \item Developed recursive repo scan, \texttt{--files}, and \texttt{--changed} via \texttt{git diff HEAD} with untracked support, enabling CI to regenerate only PR-changed files.

    \item Architected \textbf{tiered format resolution} across CLI flag, job, and global config with per-provider validation and actionable errors for unsupported formats.

\end{highlights}
\vspace{0.1cm}

\textbf{Employee Management System} \hspace{1em}\href{https://github.com/Buffden/employee-management-system}{\faGithub}\hspace{0.6em}\href{https://ems.buffden.com/}{\faLink} \hfill \textit{Dec 2024 - May 2025} \\
\textit{Enterprise-grade system for managing employees, teams, projects, and access control with production-grade deployment and observability.} \\
\textbf{Tools: } Spring Boot, Angular 19, PostgreSQL, Redis, AWS EC2, SSM, Docker, Docker Compose, Nginx, Cloudflare, GitHub Actions \\
\begin{highlights}
    \item Engineered a role-aware \textbf{JWT-based RBAC} backend across employees, departments, projects, tasks, and locations with DTO/service/repository layers.

    \item Secured production traffic with \textbf{Cloudflare-proxied DNS}, Nginx gateway routing, SSL/TLS, BCrypt auth, health checks \& containerized EC2 deployment.

    \item Built \textbf{REST APIs} with pagination, filtering, search, and dynamic dashboard metrics; added reusable \textbf{Angular Material} table views with shared components.
\end{highlights}
\vspace{0.1cm}

\textbf{AI Text Intelligence Dashboard} \hspace{1em}\href{https://github.com/Buffden/ai-text-intelligence-dashboard}{\faGithub} \hfill \textit{May 2026 - Present} \\
\textit{Technical study of LLM integration with Spring AI, exploring prompt engineering patterns, streaming architecture, and model configuration.} \\
\textbf{Tools: } Spring AI, OpenAI API (gpt-4o), Spring Boot 3.5, Java 21, Angular 19, TypeScript, SSE, RxJS \\
\begin{highlights}
    \item Experimented with JSON-enforcing system prompts, few-shot classification, chain-of-thought scratchpad, and input delimiters for injection hardening.
    \item Built \textbf{SSE streaming} via Spring AI \texttt{Flux} + \texttt{SseEmitter} consumed as Fetch \texttt{ReadableStream} in \textbf{RxJS}; built stateful chat using \textbf{ConcurrentHashMap}.
    \item Tuned \textbf{LLM config} in YAML: model selection, retry count, backoff delay, HTTP timeouts; applied full-jitter exponential backoff and \texttt{Retry-After} on 429s.
\end{highlights}

} % end small text group
\end{document}
