\documentclass[10pt, letterpaper]{article}

% --- Packages ---
\usepackage[
    ignoreheadfoot,
    top=0.7cm,
    bottom=0.7cm,
    left=0.7cm,
    right=0.7cm,
    footskip=0.5cm,
]{geometry}
\usepackage{titlesec}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 0, 0}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Harshwardhan Patil's CV},
    pdfauthor={Harshwardhan Patil},
    pdfcreator={LaTeX with RenderCV},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[scaled=0.92]{helvet}
\renewcommand\familydefault{\sfdefault}
\usepackage{changepage}
\usepackage{paracol}

% --- Page setup ---
\raggedright
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\pagenumbering{gobble}

% --- Section formatting ---
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{-1pt}{0.3cm}{0.2cm}

% --- Lists ---
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\newenvironment{highlights}{\begin{itemize}[itemsep=1pt, parsep=0pt, topsep=0pt, partopsep=0pt, leftmargin=10pt]}{\end{itemize}}
\newenvironment{onecolentry}{
  \begin{adjustwidth}{0cm}{0cm}
  \begin{itemize}[itemsep=1pt, parsep=0pt, topsep=0pt, partopsep=0pt, leftmargin=10pt]
}{
  \end{itemize}
  \end{adjustwidth}
}
\begin{document}

% --- Header ---
\begin{center}
    {\fontsize{20pt}{20pt}\selectfont \textbf{Harshwardhan Patil}} \\[6pt]
    \faMapMarker* Arlington, TX \hspace{1.2em}
    \faEnvelope\ \href{mailto:work.harshwardhanpatil@gmail.com}{work.harshwardhanpatil@gmail.com} \hspace{1.2em}
    \faPhone\ \href{tel:8179389288}{817-938-9288} \hspace{1.2em}
    \faLinkedin\ \href{https://www.linkedin.com/in/harshwardhanpatil23/}{LinkedIn} \hspace{1.2em}
    \faGithub\ \href{https://github.com/buffden}{GitHub} \hspace{1.2em}
    \faGlobe\ \href{https://buffden.github.io/buffden-portfolio/}{Portfolio}

\end{center}

{\small
\vspace{-0.5cm}
% --- Overview ---
\section{Overview}
Software Engineer with experience building and maintaining Java-based backend services and cloud-based distributed systems. Strong focus on clean API design, data correctness, system reliability, and collaborative engineering.




\vspace{-0.2cm}
% --- Technical Skills ---
\section{Technical Skills}
\begin{onecolentry}
   \item \textbf{Languages \& Frameworks:} \textbf{Java}, Spring Boot, SQL, TypeScript, JavaScript, Python
\item \textbf{APIs \& Backend:} REST APIs, DTO design, Authentication \& Authorization
\item \textbf{Databases:} PostgreSQL, MySQL, MongoDB, Redis
\item \textbf{Cloud \& DevOps:} AWS (EC2, ECS, S3, RDS), Docker, CI/CD (Jenkins, GitHub Actions)
\item \textbf{Testing:} JUnit, Mockito, SonarQube, Postman
\item \textbf{Design:} System Design, Design Patterns, SOLID principles

\end{onecolentry}

\vspace{-0.2cm}

% --- Professional Experience ---
\section{Professional Experience}

\textbf{Software Engineer, Clarivate Analytics} -- Bangalore, India \hfill \textit{Aug 2023 -- Aug 2024} \\
\begin{highlights}
    \item Developed and maintained Spring Boot REST APIs with DTO contracts \& standardized error handling, reducing breaking changes by \textbf{30\%} across releases.
    \item Built deployment pipelines using Docker, Jenkins, and Spinnaker, supporting \textbf{50+ production releases} with \textbf{zero rollbacks}.
    \item Identified performance bottlenecks in reporting services and optimized API and cache layers, reducing response latency by \textbf{25–35\%}.
    \item Implemented role-based access control across backend and frontend layers, enforcing tiered and region-based data visibility for \textbf{10+ access variants}.
    \item Designed and implemented low-latency typeahead and autocomplete services, improving search response times by \textbf{40\%} over large-scale datasets.
    \item Worked with Java concurrency primitives (thread pools, async execution) to handle parallel request processing and improve backend throughput.
    \item Diagnosed and optimized JVM-level performance issues through profiling and query tuning, improving system reliability and efficiency.
    \item Participated in peer code reviews and design discussions, focusing on maintainable code, clear API contracts, and long-term system correctness.
    \item Designed a reusable Angular table framework adopted across \textbf{3 internal teams}, reducing duplicated frontend effort and improving maintainability.
    \item Built reusable, aggregation-driven Angular chart components using D3.js, powering \textbf{15+ analytics views} for interactive reporting services.
\end{highlights}

\vspace{0.2cm}
\textbf{Associate Software Engineer, Clarivate Analytics} -- Bangalore, India \hfill \textit{Aug 2021 -- Jul 2023} \\
\begin{highlights}
    \item Optimized frontend rendering and state management for data-heavy views, improving responsiveness of interactive charts and tables by \textbf{20–25\%}.
    \item Implemented and optimized PostgreSQL schemas, queries, and indexing strategies, improving query performance by \textbf{40\%} for analytics services.
    \item Integrated Elasticsearch into Spring Boot to provide fast, advanced queries across \textbf{millions of drug records}, reducing search latency by \textbf{30\%}.
    \item Improved frontend performance by minimizing unnecessary re-renders and optimizing data-fetching patterns, resulting in \textbf{20\% faster page loads}.
    \item Migrated a legacy client-side component to an Angular 13 application, rebuilding \textbf{5+ core business flows} with a modular architecture.
    \item Implemented secure request-handling mechanisms, including JWT authentication, CORS/CSRF protection, and input validation in \textbf{multiple services}.
    \item Developed and led reusable Angular UI components, including charts and advanced table views, reused across \textbf{multiple reporting modules} consistently.
\end{highlights}
\vspace{-0.2cm}
% --- Education ---
\section{Education}
\textbf{University of Texas at Arlington}\hspace{3.3em}\textit{Master’s in Software Engineering} \hfill \textit{May 2026} \\
\textbf{BMS College of Engineering, India}\hspace{2em}\textit{Bachelor’s in Mechanical Engineering} \hfill \textit{July 2021} \\
\vspace{-0.2cm}
% --- Projects ---
\section{Projects}

\textbf{Employee Management System} \href{https://github.com/Buffden/employee-management-system}{\faGithub}\hspace{0.4em}\href{https://ems.buffden.com/}{\faGlobe} \hfill \textit{Dec 2024 – Nov 2025} \\
\textit{System for managing employees, teams, projects, and access control with reliable deployment and observability.} \\
\textbf{Tools: } Spring Boot, Angular, PostgreSQL, AWS (EC2, RDS, S3, Secrets Manager), Redis, Docker, GitHub Actions, Jenkins \\
\begin{highlights}
    \item Designed and built a backend system for employee, project, and access management, applying system design principles to enforce \textbf{RBAC}, data isolation, and deployment automation.
    \item Developed \textbf{REST APIs} for multi-entity services with pagination, filtering, and search, maintaining data correctness and API consistency.
    \item Integrated logging and monitoring into backend services to ensure data consistency, traceability, and reliable operation.
\end{highlights}
\vspace{0.2cm}

\textbf{Battle Arena – Real-Time Multiplayer Platform} \href{https://github.com/Buffden/battle-arena}{\faGithub} \hfill \textit{May 2024 – Present} \\
\textit{Multiplayer system with backend services for real-time communication and game orchestration.} \\
\textbf{Tools: } Angular, Phaser 3, Spring Boot, Node.js, MongoDB, WebSockets, Docker, AWS \\
\begin{highlights}
    \item Designed and built a distributed backend for real-time multiplayer gameplay, evaluating polling versus \textbf{WebSocket-based} communication to balance latency, consistency, and scalability.
    \item Developed a modular, terrain-aware game engine with clear separation between physics simulation, collision constraints, and gameplay rules, while defining backend service boundaries for authentication, matchmaking, and gameplay orchestration.
\end{highlights}

\vspace{0.2cm}

\textbf{AI-Powered Personal Finance Manager} \href{https://github.com/Buffden/AI-Powered-Personal-Finance-Manager}{\faGithub} \hfill \textit{Feb 2025 – Apr 2025} \\
\textit{Full-stack financial data processing system integrating live banking data with analytics and secure cloud deployment.} \\
\textbf{Tools: } Flask, Streamlit, Redis, Plaid API, Docker, AWS \\
\begin{highlights}
    \item Designed backend \textbf{REST APIs} to ingest, normalize, and categorize financial transactions from live banking data using Plaid, ensuring \textbf{secure data isolation} per user.
    \item Built \textbf{analytics pipelines} for expense aggregation and trend analysis, and delivered interactive dashboards via \textbf{secure cloud deployment} on AWS.
\end{highlights}

\vspace{-0.2cm}


% --- Certifications ---
% \section{Certifications}
% \begin{highlights}
%     \item AWS Certified Solutions Architect – Associate (2025)
%     \item AWS Certified Developer – Associate (2025)
%     \item AWS Certified Cloud Practitioner (2025)
%     \item Oracle Certified Professional: Java SE 17 Developer (2025)
% \end{highlights}

} % end small text group
\end{document}
